### 2014-11-13 tex/results.tex
results

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
algorithm at analyzing programs with unbounded complex input data in
the context of symbolic execution. To perform our evaluation
we implement a prototype of the algorithm and evaluate its efficiacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state-of-the-art symbolic execution techniques 
that support analysis of programs with complex input data types.

@@

The goal of our experiment is to evaluate the efficiacy of our
approach with respect to other state-of-the-art techniques for
symbolic execution of programs with unbounded complex data input. We
empirically evaluate the \symtxt{} algorithm by considering the
following research question: How does the cost of the \symtxt{}
algorithm compare with the \gsetxt{} (lazy), lazier, and lazier\#
algorithms?

>>>>

\section{Evaluation}
\label{sec:eval}
In this section we evaluate the effectiveness of the \symtxt{}
algorithm at analyzing programs with unbounded complex input data in
the context of symbolic execution. To perform our evaluation
we implement a prototype of the algorithm and evaluate its efficacy on
three Java data structure artifacts. We compare the results of the
\symtxt{} approach with other state-of-the-art symbolic execution techniques 
that support analysis of programs with complex input data types.

@@

The goal of our experiment is to evaluate the efficacy of our
approach with respect to other state-of-the-art techniques for
symbolic execution of programs with unbounded complex data input. We
empirically evaluate the \symtxt{} algorithm by considering the
following research question: How does the cost of the \symtxt{}
algorithm compare with the \gsetxt{} (lazy), lazier, and lazier\#
algorithms?
